\textbf{CSDS 440 Class Project: \\Adversarial Machine Learning}

### 2020-12-05 report/individual_reports/dcm101.tex
made references better

\usepackage[
backend=biber,
style=alphabetic,
citestyle=authoryear
]{biblatex}

\addbibresource{./bib/moosavidezfooli.bib} %Imports bibliography file

@@

The main algorithm that I researched for this report was DeepFool, which is an optimized attack method on data for deep neural network classifiers. This technique was first proposed by Moosavi-Dezfooli et al. in their paper, \emph{DeepFool: a simple and accurate method to fool deep neural networks} (moosavidezfooli.bib). The primary attack vector of DeepFool is to introduce instability into a classifier through adversarial perturbations, where minor changes are made to data samples that result in a classifier giving an incorrect output. What distinguishes DeepFool, however, is that it optimizes its attack to have the minimal amount of perturbations applied to the sample data that still tricks a classifier.

@@

Adversarial perturbation has seen extensive research outside of DeepFool. First thoroughly explored by Szegedy et al. in 2014, existing research aims to approximate the minimum number of perturbations required to fool a deep neural network classifier (szegedy.bib). However, their optimization method does not scale to larger datasets. These techniques are often overly-expensive in terms of computation, such as the method Nyugen et al. developed to render a data sample unrecognizable to a human, but convince a classifier to classify it with confidence (nyugen.bib). Other researchers created a fast gradient step method (goodfellow.bib), which quickly calculate approximately optimal perturbations, but this estimation can be considerably different from a more optimal solution. Figure 1 demonstrates the perturbations created by DeepFool and those created by the previously-mentioned 'fast gradient step' method. The image was originally classified as a whale, and the noise maps in the right column are the perturbations applied to that image in order for the classifier to declare the augmented image as a turtle instead. It can be clearly observed that DeepFool's perturbations are more minimal in quantity and in their affect on the base image, and was able to achieve the same desired misclassification as the gradient step method.

@@

The second algorithm that I researched, One Pixel Attack from Vargas et al.'s paper \emph{One Pixel Attack for Fooling Deep Neural Networks}, approched the same concept as DeepFool, but from a much different perspective (vargas.bib). While the DeepFool attack method would optimize how many perturbations it needs to an image in order to deceive a classifier, One Pixel Attack aims to determine a single pixel in an image that, when changed, would most likely fool the classifier. Additionally, the One Pixel Attack is a semi-black-box attack, where the only data it needs from the classifier are the output probability labels. This stands in contrast to the DeepFool attack, which needed access to the classifiers internal functions to best counter them. By operating as more of a black-box, where the internal mechanisms of the underlying classifier remain hidden, the One Pixel Attack becomes more versatile, as those data points are easier to access.

@@

\printbibliography

\end{document}

>>>>

@@

The main algorithm that I researched for this report was DeepFool, which is an optimized attack method on data for deep neural network classifiers. This technique was first proposed by Moosavi-Dezfooli et al. in their paper, \emph{DeepFool: a simple and accurate method to fool deep neural networks}. \cite{DBLP:conf/cvpr/Moosavi-Dezfooli16} The primary attack vector of DeepFool is to introduce instability into a classifier through adversarial perturbations, where minor changes are made to data samples that result in a classifier giving an incorrect output. What distinguishes DeepFool, however, is that it optimizes its attack to have the minimal amount of perturbations applied to the sample data that still tricks a classifier.

@@

Adversarial perturbation has seen extensive research outside of DeepFool. First thoroughly explored by Szegedy et al. in 2014, existing research aims to approximate the minimum number of perturbations required to fool a deep neural network classifier. \cite{DBLP:journals/corr/SzegedyZSBEGF13} However, their optimization method does not scale to larger datasets. These techniques are often overly-expensive in terms of computation, such as the method Nyugen et al. developed to render a data sample unrecognizable to a human, but convince a classifier to classify it with confidence. \cite{DBLP:journals/corr/NguyenYC14} Other researchers created a fast gradient step method \cite{DBLP:journals/corr/GoodfellowSS14}, which quickly calculate approximately optimal perturbations, but this estimation can be considerably different from a more optimal solution. Figure 1 demonstrates the perturbations created by DeepFool and those created by the previously-mentioned 'fast gradient step' method. The image was originally classified as a whale, and the noise maps in the right column are the perturbations applied to that image in order for the classifier to declare the augmented image as a turtle instead. It can be clearly observed that DeepFool's perturbations are more minimal in quantity and in their affect on the base image, and was able to achieve the same desired misclassification as the gradient step method.

@@

The second algorithm that I researched, One Pixel Attack from Vargas et al.'s paper \emph{One Pixel Attack for Fooling Deep Neural Networks}, approched the same concept as DeepFool, but from a much different perspective. \cite{DBLP:journals/tec/SuVS19} While the DeepFool attack method would optimize how many perturbations it needs to an image in order to deceive a classifier, One Pixel Attack aims to determine a single pixel in an image that, when changed, would most likely fool the classifier. Additionally, the One Pixel Attack is a semi-black-box attack, where the only data it needs from the classifier are the output probability labels. This stands in contrast to the DeepFool attack, which needed access to the classifiers internal functions to best counter them. By operating as more of a black-box, where the internal mechanisms of the underlying classifier remain hidden, the One Pixel Attack becomes more versatile, as those data points are easier to access.

@@

\bibliography{dcm101}
\printbibliography
\end{document}
